Let's talk about Thurstone & Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2024-12-07 index.qmd
section:issues,CaseV; process:write

![Thurstones cases and asumptions](/images/tables/thurstone_cases.png){#tbl-thurstone_cases width=90%}

@@

![Discrepancies in the stimuli dispersions and tehir effect on the distribution of the discriminal difference](/images/figures/dispersion.png){#fig-dispersion width=70%}

>>>>

![Thurstones cases and their asumptions](/images/tables/thurstone_cases.png){#tbl-thurstone_cases width=90%}

@@

![The Discrepancy in the dispersions of stimuli and their effect on the distribution of the discriminal difference](/images/figures/dispersion.png){#fig-dispersion width=70%}
